---
title: "Chris Notes"
author: "Chris Stantis"
date: '2022-10-19'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# Intro
I set up this Markdown notebook to keep notes related to CityWater project. I have a lot of catching up to do. 

# tapData
For tapData.csv, a data description file will be useful for readers after publication, never mind help me figure this out. 

We're going to want explanations for what got marked as clustered and not clustered (NC) and why. Going to probably want to rethink NC as a category for ```Cluster_State```, given the existence of North Carolina. 

For ```Sample_Comments``` and the phrase "isn't temporarily", do we mean temporally? 

Do we have a list of WI_Analysis_Source and easy reference?

For SLC, what's up with the outliers we're seeing between -4 and -8?

*** Changing SLC_1.1.0 to 1.10 to match system. Changing in other files as well. 

```{r exploratoryGraphs, echo = F}
ggplot(data = subset(tapData, Cluster_Location == "Salt Lake City"), aes(x = Month, y = d18O, color = Lat)) +
  geom_point(size = 3) + 
  theme_classic()

ggplot(data = subset(tapData, Cluster_Location != "NC"), aes(x = d2H, d18O, color = Cluster_Location)) + 
  geom_point(size = 3) + 
  theme_classic()
```

While looking at desc_stats1.xlsx, I think we could stand to go back to the original data. There seems to have already been some data manipulation that reviewers are going to question. Specifically, how was modality assigned in these excel files? 
I can see now the notes for how the time slices were determined, with the names in Cluster_Location_Time. How were these slices assigned?  

# G1 
Other than some typos that don't affect the code, this all looks good. I do propose we create a G0 to clean the data. This will make publication-ready data easier, as readers don't need to see our typos. 

# G2
The coordinate reference system ```us_states``` is EPSG:4269. Is that okay when you're working in 4326? I'm not familiar with coordinate systems and EPSG codes. 

# G7
Created ordered factor for SLC data so it goes from 1.1 - 1.11 properly. Original had 1.1, 1.10, 1.11, 1.2....

